---
title: "EDA"
output: html_document
---

# Setting{.tabset .tabset-fade .tabset-pills}

## knitr option

```{r reset, include=FALSE}
# reset
rm(list = ls())
```

```{r set up, message=FALSE}
# set directory
setwd("~/Desktop/Elo_kaggle/") 
# max.print 
options(max.print="200", digits=5)
# Global options
library(knitr)
opts_chunk$set(echo=TRUE,
               # cache = FALSE,
	             prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## Library package

```{r package, message=FALSE}
library(tidyverse)
library(summarytools) # summary easily for EDA
library(skimr)
library(feather)
library(lubridate)
```

## Load funciton

- csv fileをfeather fileにする.

```{r}
# source('~/Desktop/Elo_kaggle/script/convert_to_feather.R')
```

## ggplot themes

```{r}
# set ggplot theme
library(ggplot2)
library(ggthemes)
# theme_set(theme_classic(base_size = 14, base_family = "HiraKakuPro-W3")) # 日本語用
theme_set(theme_classic(base_size = 18,base_family = "Helvetica")) # 英語用
```

## Import csv

- Import raw data from `csv/~.csv`
- Define missing values: na = c("XNA","NA","","NaN","?",...)
- Convert charcter's columns into factor's columns 
- Delete duplicate column names and change them to lower case

```{r}
train <- read_feather("~/Desktop/Elo_kaggle/input/feather/train.feather")
test <- read_feather("~/Desktop/Elo_kaggle/input/feather/test.feather")
transactions <- read_feather("~/Desktop/Elo_kaggle/input/feather/historical_transactions.feather")
new_transactions <- read_feather("~/Desktop/Elo_kaggle/input/feather/new_merchant_transactions.feather")
merchants <- read_feather("~/Desktop/Elo_kaggle/input/feather/merchants.feather")
sample_submit <- read_feather("~/Desktop/Elo_kaggle/input/feather/sample_submission.feather")
```

# EDA{.tabset .tabset-fade .tabset-pills}

## glimpse 

```{r}
train %>% glimpse()
test %>% glimpse()
transactions %>% glimpse()
new_transactions %>% glimpse()
merchants %>% glimpse()
```

## skimr

```{r}
skimr::skim_to_wide(train) %>% kable()
skimr::skim_to_wide(test) %>% kable()
skimr::skim_to_wide(transactions) %>% kable()
skimr::skim_to_wide(new_transactions) %>% kable()
merchants %>% 
  mutate_if(is.numeric,funs(ifelse(is.finite(.), ., NA_real_))) %>% View
  skimr::skim_to_wide() %>% 
  kable()
```

## summarytools

```{r}
dfSummary(train) %>% view(method = "render")
dfSummary(test) %>% view(method = "render")
dfSummary(transactions) %>% view(method = "render")
dfSummary(new_transactions) %>% view(method = "render")
merchants %>% 
  mutate_if(is.numeric,funs(ifelse(is.finite(.), ., NA_real_))) %>% 
  dfSummary() %>% 
  view(method = "render")
```

# 基礎集計

## train

- -30 < くらいに外れ値がある.

```{r}
train %>% 
  ggplot(aes(x=target)) +
  geom_histogram(bins = 200)
```

## transaction

- purchase_date

3ヶ月以上ない??

```{r}
tmp <- transactions %>% 
  group_by(card_id) %>% 
  summarise(interval =  max(purchase_date) - min(purchase_date))
tmp %>% 
  mutate(interval = interval %>% as.numeric() %/% 30) %>% 
  group_by(interval) %>% 
  summarise(count = n()) %>% 
  t() %>% 
  as.data.frame() %>% 
  kable(format="markdown")
```

- month_lag

```{r}
# month_lagの出現回数
tmp <- transactions %>% 
  distinct(card_id, month_lag) %>% 
  group_by(month_lag) %>% 
  summarise(num = n())
as.data.frame(t(tmp)) %>% kable(format="markdown")

# card_idごとの最新のmonth_lag情報
tmp <- transactions %>% 
  group_by(card_id) %>% 
  summarise(max = max(month_lag), min = min(month_lag))
# maxの集計
tmp %>% 
  group_by(max) %>% 
  summarise(count=n()) %>%
  t() %>% 
  as.data.frame() %>% 
  kable(format="markdown")
# minの集計
tmp %>% 
  group_by(min) %>% 
  summarise(count=n()) %>%
  t() %>% 
  as.data.frame() %>% 
  kable(format="markdown")
```

- purchase_amount

正規化された購入金額??(1つ大きな外れ値), 周期性がある. 

```{r}
transactions %>% 
  filter(purchase_amount < 200000) %>% 
  group_by(hours = floor_date(purchase_date,"hour")) %>% 
  summarise(money = mean(purchase_amount)) %>% 
  ggplot(aes(x=hours,y=money)) +
  geom_line()
```

## merchant_id
