---
title: "EDA"
output: html_document
---

# Setting{.tabset .tabset-fade .tabset-pills}

## knitr option

```{r reset, include=FALSE}
# reset
rm(list = ls())
```

```{r set up, message=FALSE}
# set directory
setwd("~/Desktop/Elo_kaggle/") 
# max.print 
options(max.print="200", digits=5)
# Global options
library(knitr)
opts_chunk$set(echo=TRUE,
               # cache = FALSE,
	             prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## Library package

```{r package, message=FALSE}
library(tidyverse)
library(summarytools) # summary easily for EDA
library(skimr)
library(feather)
```

## Load funciton

- csv fileをfeather fileにする.

```{r}
# source('~/Desktop/Elo_kaggle/script/convert_to_feather.R')
```

## ggplot themes

```{r}
# set ggplot theme
library(ggplot2)
library(ggthemes)
# theme_set(theme_classic(base_size = 14, base_family = "HiraKakuPro-W3")) # 日本語用
theme_set(theme_classic(base_size = 18,base_family = "Helvetica")) # 英語用
```

## Import csv

- Import raw data from `csv/~.csv`
- Define missing values: na = c("XNA","NA","","NaN","?",...)
- Convert charcter's columns into factor's columns 
- Delete duplicate column names and change them to lower case

```{r}
train <- read_feather("~/Desktop/Elo_kaggle/input/feather/train.feather")
test <- read_feather("~/Desktop/Elo_kaggle/input/feather/test.feather")
transactions <- read_feather("~/Desktop/Elo_kaggle/input/feather/historical_transactions.feather")
new_transactions <- read_feather("~/Desktop/Elo_kaggle/input/feather/new_merchant_transactions.feather")
merchants <- read_feather("~/Desktop/Elo_kaggle/input/feather/merchants.feather")
sample_submit <- read_feather("~/Desktop/Elo_kaggle/input/feather/sample_submission.feather")
```

# EDA{.tabset .tabset-fade .tabset-pills}

## glimpse 

```{r}
train %>% glimpse()
test %>% glimpse()
transactions %>% glimpse()
new_transactions %>% glimpse()
merchants %>% glimpse()
```

## skimr

```{r}
skimr::skim_to_wide(train) %>% kable()
skimr::skim_to_wide(test) %>% kable()
skimr::skim_to_wide(transactions) %>% kable()
skimr::skim_to_wide(new_transactions) %>% kable()
skimr::skim_to_wide(merchants) %>% kable()
```

## summarytools

```{r}
dfSummary(train) %>% view(method = "render")
dfSummary(test) %>% view(method = "render")
dfSummary(transactions) %>% view(method = "render")
dfSummary(new_transactions) %>% view(method = "render")
dfSummary(merchants) %>% view(method = "render")
```


